Analysis paper

### 2021-06-25 analysis/analysis.Rmd
update plota

```{r}
dailytruth_data %>%
  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
                target_end_date <= max(forecast_dates$full_hub_period)) %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_point(size = 0.3, alpha = 0.4) + 
  geom_line(size = 0.5, alpha = 0.4) + 
  geom_line(data = truth_data, aes(y = true_value / 7)) + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  labs(y = "Observed values", x = "Date") + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
                            max(forecast_dates$full_hub_period))) + 
  theme_minimal()

ggsave(here("analysis", "plots", "daily_truth.png"))
```

@@

  p_cov50 <- scores[range %in% c(50)] %>%
    plot_helper(y = "coverage") + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    labs(y = "Coverage - 50% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_cov90 <- scores[range %in% c(90)] %>%
    plot_helper(y = "coverage") + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    labs(y = "Coverage - 50% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

>>>>

```{r}
df <- copy(dailytruth_data)[
  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
]

weeklytruth <- copy(truth_data)[
  , target_location := paste0(str_to_title(target_type), "s in ", location_name)
]

df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  # geom_point(size = 0.3, alpha = 0.4) + 
  # geom_line(size = 0.5, alpha = 0.4) + 
  geom_col(fill = "lightsteelblue", color = "white") + 
  geom_line(data = weeklytruth, aes(y = true_value / 7)) + 
  geom_point(data = weeklytruth, aes(y = true_value / 7), size = 0.3) +
  facet_wrap( ~ target_location, scales = "free", ncol = 1) + 
  labs(y = "Observed values", x = "Date") + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
                          max(forecast_dates$full_hub_period + 21))) + 
  theme_minimal()

ggsave(here("analysis", "plots", "daily_truth.png"), width = 10, height = 8)
```

@@

  p_cov50 <- scores[range %in% c(50)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    labs(y = "Coverage - 50% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_cov90 <- scores[range %in% c(90)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    labs(y = "Coverage - 50% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)
